Sketching for Density Estimation

### 2018-12-08 density.tex
cleaner table

\newcommand{\ccc}[1]{\parbox}
\begin{table}[htp]
\caption{default}
\begin{center}
\begin{tabular}{|c|c|c|c|} \hline
Problem				& $f$ 							& $R_m$ 		& $K_m$ \\ \hline
Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 	& $1/\sqrt{m}$	& $1/m$ \\ \hline
Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  	& $1/\sqrt{m}$	& $1/m$ \\ \hline
Matrix Sketching		& $f(x, q) = \langle x,q \rangle ^2$ where $q,x\in \R^d$	& $1/\sqrt{m}$	& $\min\{\sqrt{d}/m,1/\sqrt{m}\}$ \\ \hline
Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ or any other positive kernel (see \cite{}) & ?	$\sqrt{m}$ ? \\ \hline
Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 		& ?	 ? \\ \hline
Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else	& ?	& ? \\ \hline
Graph Laplacian 		& $f(x, q) = q^T L_x q = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$ and $q \in \R^n$ & ?	& ? \\ \hline
Entry-wise Matrix Approximation  & $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ & ?	& ? \\ \hline
\end{tabular}
\end{center}
\label{default}
\end{table}%

>>>>

\newcommand{\ccc}[1]{\parbox}
\begin{table}[htp]
\caption{default}
\begin{center}
\begin{tabular}{|c|c|c|c|} \hline
Problem				& $f$ 											& $R_m$ 			& $K_m$ \\ \hline
Counting 				& $f(x, q) = 1$ if $x=q$ and zero else 					& $1/\sqrt{m}$		& $1/m$ \\ \hline
Quantiles				& $f(x, q) = 1$ if $x\le q$ and zero else  					& $1/\sqrt{m}$		& $1/m$ \\ \hline
Column Slection		& $f(x, q) = \langle x,q \rangle ^2$ where  $q,x\in \R^d$		& $1/\sqrt{m}$		& $\sqrt{d}/m$ \\ \hline
Kernel Density 			& $f(x, q) = \exp(- \|x-y\|_2^2/\sigma^2)$ 					& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
Logistic Regression     	& $f(x, q) = \log(1 + \exp(q^T x))$ 						& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
Hinge Regression     		& $f(x, q) = [1-q^T x]_+$								& $1/\sqrt{m}$ 		& $\sqrt{d}/m$ \\ \hline
Linear Classification		& $f(x,q) = 1$ if $x^Tq > 0$ and $0$ else					& ?				& ? \\ \hline
Graph Laplacian 		& $f(x, q) = w_{ij}(q_i - q_i)^2$ for $x = (w_{ij},i,j)$, $q \in \R^n$ & ?				& ? \\ \hline
Matrix Approximation  	& $f(x, q) = w_{ij}u_iv_j$ for $x = (a_{ij},i,j)$  and $q = (u,v)$ 	& ?				& ? \\ \hline
\end{tabular}
\end{center}
\label{default}
\end{table}%
